Frustratingly easy multi-domain, multilingual translation with latent multi-task group dropout

### 2021-11-05 2022/acl/acl_latex.tex
adding reference
local merges
local changes

@@

According to Table \ref{tab:multilingual}, \system{LAMGD} shows a boost of 0.42, 0.33, ,0.32 in average over the multilingual \system{Transformer} in O2M-related, M2O-related, O2M-diverse, M2O-diverse respectively. Significant gains are observed in \domain{bel}, \domain{glg} (both direction), \domain{hin} and \domain{bos} (O2M direction).

>>>>

\citet{Christopher21efficiently}

@@

According to Table \ref{tab:multilingual}, \system{LaMGD} shows a boost of 0.42, 0.33, 0.32 in average over the multilingual \system{Transformer} in O2M-related, M2O-related, M2O-diverse respectively. Significant gains are observed in \domain{bel}, \domain{glg} (both direction), \domain{hin} and \domain{bos} (O2M direction).
